% define document type, font-size, and paper dimensions
\documentclass[11pt, letterpaper]{article}
% set up image package & path
\usepackage{graphicx}
% subcaption for multi-figures
\usepackage{subcaption}
% adds a header onto every page
\usepackage{fancyhdr}
% adds indent to paragraph after section header
\usepackage{indentfirst}
% make margins 1in
\usepackage[total={6.5in,8.75in},
top=1.25in, left=1in]{geometry}
% add hyperlinks
\usepackage{hyperref}

% set up page style & graphic path
\pagestyle{fancy}
\graphicspath{{./images/}}

% Resize table rows
\renewcommand{\arraystretch}{1.75}

% Set up title page
\renewcommand{\maketitle}{
    \begin{titlepage}
        % Set up title page
        \centering
        \huge{\textbf{ECS 171 Group 10 Project}} \par
        \vspace{.5cm}
        % group leader
        \large{Leader: Ryan Yu} \par
        \vspace{.5cm}
        % group members
        \normalfont{Amira Basyouni, Calvin Chen, Alexis Lydon, Tianming Tan} \par
        \vspace{.5cm}
        % date
        \today
    \end{titlepage}
}

% set up header
\fancyhf{} % clear all header and footer fields
\lhead{ECS 171 Group Project} % left header
\rhead{\thepage} % right header
%\fancyhfoffset[LR]{1cm} % increase left, right margin by 1cm

\begin{document}
    \maketitle
    
    \newpage

    \section*{Problem Statement}
    As a student, we are in a battle between the many stressors we have in our lives 
    and our strive towards academic success. We are faced with deadlines, exams, and 
    the pressure to perform well. These factors can have a negative impact on our 
    quality of learning and thus hinder our progress towards acquiring a degree and 
    entering the workforce. Our team would like to alleviate this problem using sleep. 
    We would like to predict the effects poor sleep quality can have on our stress 
    levels. Would longer sleep duration result in a decrease in stress? After we 
    analyze our data, we will be able to confirm the correlation between those two 
    attributes. We will also look into other factors affecting stress such as physical 
    activity, occupation, and blood pressure. By finding various correlations, we can 
    narrow down the factors affecting stress and ultimately propose a healthy set of 
    habits to help manage our mental health. The data will involve ages that vary from 
    27 to 59 years of age. Although it does not cover the typical age of a college 
    student, our analysis can still help us build awareness that would last us for 
    years to come.

    \section*{Dataset}
    The dataset being used in this project is the "Sleep Health and Lifestyle Dataset" 
    by Laksika Tharmalingam on Kaggle. This dataset is structured as a CSV file and contains 
    400 rows and 13 columns, featuring a wide array of sleep and lifestyle variables. These variables 
    encompass information such as gender, age, occupation, sleep duration, sleep quality, physical 
    activity, stress levels, BMI category, blood pressure, heart rate, daily steps, and sleep disorder 
    status. We selected this dataset because, as students, we can readily relate to the common sleep-related 
    challenges that many of us encounter. Our project places a particular emphasis on exploring the relationship 
    between sleep and stress, rendering a dataset that focuses on sleep and health the most apt choice. A limitation 
    of the dataset is its synthetic nature, generated artificially rather than 
    from real-world observations. While it may lack some real-world nuances, high-quality synthetic data can 
    effectively train and test machine learning models in this context. Here is the link
    of our dataset for further reference: \href{https://www.kaggle.com/datasets/uom190346a/sleep-health-and-lifestyle-dataset/data}{Sleep Health and Lifestyle Dataset}

    
    \section*{Goals}
    In this machine learning project centered on the intersection of sleep health and stress, 
    our primary objective is to examine the correlation between key attributes such as sleep duration,
    sleep quality, BMI, blood pressure, and occupation, and their influence on stress levels. 
    This analysis will help us better understand and predict the dynamics between these factors and 
    identify the attributes that have the most significant impact on stress levels. 
    As an integral part of the project, we will develop an accurate regression model for stress prediction 
    based on the highly correlated attributes in our dataset. Our last goal, which is somewhat a reach goal 
    due to its complexity, is to determine the extent to which additional sleep reduces an individual's stress level 
    and the optimal duration for stress reduction. These defined project goals will serve as a structured guide 
    throughout our research, data collection, analysis, and model development, enabling us to gain valuable insights 
    into the complex relationship between sleep health and stress levels while delivering practical solutions and predictions for this area of health.

    \newpage

    \section*{Project Timeline}
    For our project, we plan to roughly follow the timeline below:
    
    \begin{table}[htbp]
        \centering
        \begin{tabular}{l|c|c|c}
            \hline \hline
            \multicolumn{4}{c}{\textbf{Project Timeline}} \\ % resizes n columns into one
            \hline \hline
            \multicolumn{1}{c|}{\textbf{Task}} & \textbf{Start Date} & \textbf{End Date} & \textbf{Duration (days)} \\
            \hline
            Background/Literature Review & Oct. 16 & Oct. 22 & 7 \\
            \hline
            Exploratory Data Analysis & Oct. 23 & Oct. 29 & 7 \\
            \hline
            Developing prediction models & Oct. 30 & Nov. 5-8 & 7-10 \\
            \hline
            Evaluation of the model and testing performance & Nov. 6-9 & Nov. 12-14 & 7-9 \\
            \hline
            Developing front-end to display and run models & Nov. 13-15 & Nov. 19-21 & 7 \\
            \hline
            Finish Report and Minor Adjustments & Nov. 20-22 & Nov. 23-25 & 4 \\
            \hline
            Presentation Practice & Nov. 24-26 & Nov. 28-30 & 5 \\
            \hline \hline
        \end{tabular}
        \caption{Tasks, Start and End Dates, and Planned Duration}
        \label{tab:timeline}
    \end{table}

    \textbf{\underline{Task Breakdown}}
    \begin{enumerate}
        \item Background/Literature Review: Research our problem and describe it scientifically
        \item Exploratory Data Analysis: Understanding our dataset and filtering out noise
        \item Developing prediction models: Creating 3+ models to quantify and predict desired outcomes
        \item Evaluation of the model and testing performance: Testing our models and deciding on the best performing one
        \item Developing front-end to display and run models: Invoke our models and display results
        \item Finish Report and Minor Adjustments: Clean up our code and final report paper
        \item Presentation Practice: Practice our presentation and prepare for questions
    \end{enumerate}

\end{document}
